### 2024-09-20 output/paper.qmd
clean the dataset and create some visualizations

---
title: "toronto_fire_incidents_analysis"
author: "Boxuan Yi"
format: pdf
---

```{r}
library(dplyr)
library(tidyverse)
library(here)
library(janitor)
library(knitr)
library(ggplot2)
```

```{r}
data_cleaned <- read_csv(file = here("../inputs/data/data_cleaned.csv"))
```

```{r}
data_cleaned |>
  group_by(occurrence_month) |>
  summarise(n = n()) |>
  ggplot(mapping = aes(x = occurrence_month, y = n)) +
  geom_line(color = "tomato4") +
  geom_point(color = "black") +
  labs(x = "Occurrence Month", y = "Number of Observations", title = "Monthly Occurrences of Crimes From 2018 to 2023") +
  scale_x_continuous(breaks = 1:12) +  # Set x-axis breaks to show only 1 to 12
  theme_minimal()

```

```{r}
data_cleaned |>
  ggplot(mapping = aes(x = occurrence_year, fill = race_bias)) +
  geom_bar() +
  labs(x = "Year Offence Occurred", y = "Number of Observations", fill = "Race Bias") +
  theme(legend.position = "right") +
  scale_x_continuous(breaks = seq(2018, 2023, by = 1))
```

```{r}
data_cleaned |>
  ggplot(mapping = aes(x = occurrence_year, fill = religion_bias)) +
  geom_bar() +
  labs(x = "Year Offence Occured", y = "Number of Observations", fill = "Religion Bias") +
  theme(legend.position = "right") +
  scale_x_continuous(breaks = seq(2018, 2023, by = 1))
```

```{r}
data_cleaned |>
  ggplot(mapping = aes(x = occurrence_year, fill = location_type)) +
  geom_bar() +
  labs(x = "Year Offence Occured", y = "Number of Observations", fill = "Location Type of the Offence") +
  theme(legend.position = "right") +
  scale_x_continuous(breaks = seq(2018, 2023, by = 1))

data_cleaned |>
  ggplot(mapping = aes(x = division_area, fill = location_type)) +
  geom_bar() +
  labs(x = "Division Area", y = "Number of Observations", fill = "Location Type of the Offence") +
  theme(legend.position = "right") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```

```{r}
data_cleaned |>
  ggplot(mapping = aes(x = location_type, fill = primary_offence_simplified)) +
  geom_bar() +
  labs(x = "Location Type", y = "Number of Observations", fill = "Primary Offence") +
  theme(legend.position = "right") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

```{r}
data_cleaned |>
  group_by(mental_or_physical_disability) |>
  summarise(count = n()) |>
  rename("Mental or Physical Disability Bias" = mental_or_physical_disability, "Count" = count) |>
  kable()
```

```{r}
data_cleaned |>
  group_by(age_bias) |>
  summarise(count = n()) |>
  rename("Age Bias" = age_bias, "Count" = count) |>
  kable()
```

### 2024-09-20 scripts/01-download_data.R

@@ -1,0 +1,34 @@
+#### Preamble ####
+# Purpose: Download and read in the hate crimes data from Open Data Toronto
+# Author: Boxuan Yi
+# Email: boxuan.yi@mail.utoronto.ca
+# Date: 15 September 2024
+# Prerequisites: None
+
+# install.packages('opendatatoronto')
+# install.packages('dylyr')
+# install.packages('tidyverse')
+# install.packages('here')
+# install.packages('janitor')
+# install.packages('knitr')
+# install.packages('ggplot2')
+
+library(opendatatoronto)
+library(dplyr)
+library(tidyverse)
+library(here)
+library(janitor)
+
+# get package
+package <- show_package("hate-crimes-open-data")
+
+# get all resources for this package
+resources <- list_package_resources("hate-crimes-open-data")
+datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
+data_raw <- filter(datastore_resources, row_number()==1) %>% get_resource()
+
+# write data
+write_csv (
+  x = data_raw,
+  file = "downloads/hate_crime/inputs/data/data_raw.csv"
+)

### 2024-09-20 scripts/02-clean_data.R

@@ -1,0 +1,94 @@
+#### Preamble ####
+# Purpose: Clean the raw hate crimes data from Open Data Toronto
+# Author: Boxuan Yi
+# Email: boxuan.yi@mail.utoronto.ca
+# Date: 15 September 2024
+# Prerequisites: None
+
+library(dplyr)
+library(tidyverse)
+library(here)
+library(janitor)
+library(knitr)
+
+data_raw <- read_csv(file = here("../inputs/data/data_raw.csv"))
+
+data_cleaned <- clean_names(data_raw)
+data_cleaned <- na.omit(data_cleaned)
+data_cleaned$occurrence_month <- as.numeric(substr(data_cleaned$occurrence_date, 6, 7))
+
+data_cleaned <- data_cleaned |>
+  filter(!(religion_bias %in% c("Christian Orthodox, Jewish", "Jewish, Muslim"))) |>
+  mutate(religion_bias = case_when(
+    religion_bias %in% c("Anglican", "Other Christian Religion", "Christian Orthodox") ~ "Christian",
+    TRUE ~ religion_bias
+  ))
+
+data_cleaned <- data_cleaned |>
+  filter(!(race_bias %in% c("Black, East/Southeast Asian", "Black, Indigenous", "Black, South Asian", 
+                            "Black, White", "East/Southeast Asian, South Asian, Black", 
+                            "Indigenous, East/Southeast Asian", "White, East/Southeast Asian", 
+                            "Other race not mentioned"))) |>
+  mutate(race_bias = case_when(
+    race_bias %in% c("Black") ~ "Black",
+    race_bias %in% c("East/Southeast Asian") ~ "East/Southeast Asian",
+    race_bias %in% c("Indigenous") ~ "Indigenous",
+    race_bias %in% c("Latino") ~ "Latino",
+    race_bias %in% c("Middle Eastern") ~ "Middle Eastern",
+    race_bias %in% c("South Asian") ~ "South Asian",
+    race_bias %in% c("White") ~ "White",
+    TRUE ~ race_bias
+  ))
+
+data_cleaned <- data_cleaned |>
+  mutate(location_type = case_when(
+    location_type %in% c("Government Building", "Government Building (Courthouse, Museums, Parliament Building, etc.)", "Non-Commercial/Non for Profit") ~ "Government/Public Buildings",
[…]

### 2024-09-20 scripts/03-test_data.R

@@ -1,0 +1,19 @@
+#### Preamble ####
+# Purpose: Test the cleaned hate crimes data
+# Author: Boxuan Yi
+# Email: boxuan.yi@mail.utoronto.ca
+# Date: 17 September 2024
+# Prerequisites: None
+
+library(here)
+library(dplyr)
+library(tidyverse)
+
+data_cleaned <- read_csv(
+  file = here("downloads/hate_crime/inputs/data/data_cleaned.csv"))
+
+any(duplicated(data_cleaned$id)) == FALSE
+data_cleaned$occurrence_year |> min() >= 2018
+data_cleaned$occurrence_month |> class() == "numeric"
+data_cleaned$division |> unique()
+all(unique(data_cleaned$division_area) %in% c("Etobicoke-York","Toronto-East York","North York","Etobicoke","Scarborough","Other"))

### 2024-09-20 scripts/download.R
Delete scripts/download.R

@@ -1,18 +1,0 @@
-install.packages('opendatatoronto')
-install.packages('dylyr')
-library(opendatatoronto)
-library(dplyr)
-
-# get package
-package <- show_package("64a26694-01dc-4ec3-aa87-ad8509604f50")
-package
-
-# get all resources for this package
-resources <- list_package_resources("64a26694-01dc-4ec3-aa87-ad8509604f50")
-
-# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
-datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
-
-# load the first datastore resource as a sample
-data_original <- filter(datastore_resources, row_number()==1) %>% get_resource()
-head(data_original)

### 2024-09-20 scripts/00-simulate_data.R
Create a simulated data and several tests

@@ -1,0 +1,72 @@
+#### Preamble ####
+# Purpose: Simulate the data used for analyzing hate crimes in Toronto
+# Author: Boxuan Yi
+# Email: boxuan.yi@mail.utoronto.ca
+# Date: 19 September 2024
+# Prerequisites: None
+
+library(tibble)
+
+# Define the lists
+race <- c("None", "Black", "Indigenous", "White", 
+          "East/Southeast Asian", "Middle Eastern", 
+          "South Asian", "Latino")
+
+religion <- c("Jewish", "None", "Muslim", "Christian", 
+              "Sikh", "Catholic", "Hindu")
+
+primary_offence <- c("Hate Crimes", "Property Crimes", "Assault", 
+                     "Threats and Harassment", "Other Offences", 
+                     "Sexual Offences", "Violent Crimes")
+
+division_area <- c("Etobicoke-York", "Toronto-East York", 
+                   "North York", "Scarborough", "Other", 
+                   "Etobicoke")
+
+location_type <- c("Commercial/Business", "Public Spaces/Transportation", 
+                   "Government/Public Buildings", "Residential", 
+                   "Educational", "Healthcare", "Religious")
+
+
+# Simulate the data using the lists
+set.seed(123)
+simulated_data <-
+  tibble(
+    "ID" = 1:500,
+    "occurrence_year" = sample(2018:2023, 500, replace = TRUE),
+    "occurrence_month" = sample(1:12, 500, replace = TRUE),
+    "location_type" = sample(location_type, 500, replace = TRUE),
+    "race_bias" = sample(race, 500, replace = TRUE),
+    "religion_bias" = sample(religion, 500, replace = TRUE),
+    "primary_offence_simplified" = sample(primary_offence, 500, replace = TRUE),
+    "division_area" = sample(division_area, 500, replace = TRUE),
+    "age_bias" = sample(c("NO", "YES"), 500, replace = TRUE, prob = c(0.95, 0.05)),
+    "mental_or_physical_disability" = sample(c("NO", "YES"), 500, replace = TRUE, prob = c(0.95, 0.05))
+  )
+
+
+# Test the simulated data
+class(simulated_data$occurrence_month) == 'integer'
+simulated_data$occurrence_year |> min() >= 2018
+simulated_data$occurrence_year |> max() <= 2023
+
+all(unique(simulated_data$division_area) %in% c("Etobicoke-York", "Toronto-East York", 
+                                              "North York", "Etobicoke", 
+                                              "Scarborough", "Other"))
+
[…]

### 2024-09-20 scripts/02-clean_data.R

@@ -2,7 +2,7 @@
 # Purpose: Clean the raw hate crimes data from Open Data Toronto
 # Author: Boxuan Yi
 # Email: boxuan.yi@mail.utoronto.ca
-# Date: 15 September 2024
+# Date: 19 September 2024
 # Prerequisites: None
 
 library(dplyr)
@@ -11,12 +11,14 @@ library(here)
 library(janitor)
 library(knitr)
 
+# Read the raw dataset
 data_raw <- read_csv(file = here("../inputs/data/data_raw.csv"))
 
 data_cleaned <- clean_names(data_raw)
 data_cleaned <- na.omit(data_cleaned)
 data_cleaned$occurrence_month <- as.numeric(substr(data_cleaned$occurrence_date, 6, 7))
 
+# Modify the religion bias column
 data_cleaned <- data_cleaned |>
   filter(!(religion_bias %in% c("Christian Orthodox, Jewish", "Jewish, Muslim"))) |>
   mutate(religion_bias = case_when(
@@ -24,6 +26,7 @@ data_cleaned <- data_cleaned |>
     TRUE ~ religion_bias
   ))
 
+# Modify the race bias column
 data_cleaned <- data_cleaned |>
   filter(!(race_bias %in% c("Black, East/Southeast Asian", "Black, Indigenous", "Black, South Asian", 
                             "Black, White", "East/Southeast Asian, South Asian, Black", 
@@ -40,6 +43,7 @@ data_cleaned <- data_cleaned |>
     TRUE ~ race_bias
   ))
 
+# Modify the location type column
 data_cleaned <- data_cleaned |>
   mutate(location_type = case_when(
     location_type %in% c("Government Building", "Government Building (Courthouse, Museums, Parliament Building, etc.)", "Non-Commercial/Non for Profit") ~ "Government/Public Buildings",
@@ -52,6 +56,7 @@ data_cleaned <- data_cleaned |>
     TRUE ~ location_type  # If any unhandled cases, keep original
   ))
 
+# Create a simplified column that describes the primary offence
 data_cleaned <- data_cleaned |>
   mutate(primary_offence_simplified = case_when(
     primary_offence %in% c("Wilful Promotion of Hatred", "Public Incitement of Hatred", "Advocating Genocide") ~ "Hate Crimes",
@@ -63,7 +68,7 @@ data_cleaned <- data_cleaned |>
     TRUE ~ "Other Offences"  # for any other offences not categorized
   ))
 
-
[…]

### 2024-09-20 scripts/03-test_data.R

@@ -2,7 +2,7 @@
 # Purpose: Test the cleaned hate crimes data
 # Author: Boxuan Yi
 # Email: boxuan.yi@mail.utoronto.ca
-# Date: 17 September 2024
+# Date: 19 September 2024
 # Prerequisites: None
 
 library(here)
@@ -10,10 +10,24 @@ library(dplyr)
 library(tidyverse)
 
 data_cleaned <- read_csv(
-  file = here("downloads/hate_crime/inputs/data/data_cleaned.csv"))
+  file = here("../inputs/data/data_cleaned.csv"))
 
 any(duplicated(data_cleaned$id)) == FALSE
 data_cleaned$occurrence_year |> min() >= 2018
 data_cleaned$occurrence_month |> class() == "numeric"
-data_cleaned$division |> unique()
-all(unique(data_cleaned$division_area) %in% c("Etobicoke-York","Toronto-East York","North York","Etobicoke","Scarborough","Other"))
+data_cleaned$occurrence_date |> class() == "Date"
+
+all(unique(data_cleaned$division_area) %in% c("Etobicoke-York",
+                                              "Toronto-East York","North York",
+                                              "Etobicoke","Scarborough","Other"))
+all(unique(data_cleaned$race_bias) %in% c("None", "Black", "Indigenous", "White", 
+                                          "East/Southeast Asian", "Middle Eastern", 
+                                          "South Asian", "Latino"))
+all(unique(data_cleaned$religion_bias) %in% c("Jewish", "None", "Muslim", 
+                                              "Christian", "Sikh", "Catholic", "Hindu"))
+all(unique(data_cleaned$mental_or_physical_disability) %in% c("NO", "YES"))
+all(unique(data_cleaned$age_bias) %in% c("NO","YES"))
+all(unique(data_cleaned$primary_offence_simplified) %in% c("Hate Crimes", "Property Crimes", 
+                                                           "Assault", "Threats and Harassment", 
+                                                           "Other Offences", "Sexual Offences", 
+                                                           "Violent Crimes"))

### 2024-09-20 output/paper.qmd
finish visualizations

@@
 ---
-
+Paper 1
 ```{r}
+#| include: false
 library(dplyr)
@@
 ```{r}
+#| include: false
 data_cleaned <- read_csv(file = here("../inputs/data/data_cleaned.csv"))
@@
 ```{r}
+#| message: false
+#| echo: false
+#| warning: false
+#| label: fig-month
+#| fig-cap: Monthly Occurrences of Hate Crimes in Toronto From 2018 to 2023
 data_cleaned |>
@@
   geom_point(color = "black") +
-  labs(x = "Occurrence Month", y = "Number of Observations", title = "Monthly Occurrences of Crimes From 2018 to 2023") +
+  labs(x = "Occurrence Month", y = "Number of Observations") +
   scale_x_continuous(breaks = 1:12) +  # Set x-axis breaks to show only 1 to 12
@@
 ```{r}
+#| message: false
+#| echo: false
+#| warning: false
+#| label: fig-race
+#| fig-cap: Trends in Hate Crimes by Race Bias From 2018 to 2023
 data_cleaned |>
@@
 ```{r}
+#| message: false
+#| echo: false
+#| warning: false
+#| label: fig-religion
+#| fig-cap: Trends in Hate Crimes by Religion Bias From 2018 to 2023
 data_cleaned |>
@@
   geom_bar() +
-  labs(x = "Year Offence Occured", y = "Number of Observations", fill = "Religion Bias") +
+  labs(x = "Year Offence Occurred", y = "Number of Observations", fill = "Religion Bias") +
   theme(legend.position = "right") +
@@
 ```{r}
+#| message: false
+#| echo: false
+#| warning: false
+#| label: fig-location_year
+#| fig-cap: Trends in Hate Crimes by Location Type of the Offence From 2018 to 2023
 data_cleaned |>
@@
   scale_x_continuous(breaks = seq(2018, 2023, by = 1))
+```
+
+```{r}
+#| label: fig-location
+#| fig-cap: Number of Hate Crimes by Primary Offence Across Different Areas
+#| echo: false
+#| warning: false
+#| message: false
+#| layout-ncol: 1
+#| fig-subcap: ["Distribution of Hate Crimes by Division Area and Location Type", "Distribution of Primary Offence by Location Type"]
 
@@
 
-```
-
-```{r}
 data_cleaned |>
@@
 ```{r}
+#| message: false
+#| echo: false
+#| warning: false
+#| label: tbl-disability
+#| tbl-cap: The Number of Hate Crimes Based on Suspect’s Perception of Victim’s Mental or Physical Disability
 data_cleaned |>
@@
 ```{r}
+#| message: false
+#| echo: false
+#| warning: false
+#| label: tbl-clean_mci_data
+#| tbl-cap: The Number of Hate Crimes Based on Suspect’s Perception of Victim’s Age
 data_cleaned |>

### 2024-09-21 output/paper.qmd
first draft and modify the scripts

@@
 ---
-title: "toronto_fire_incidents_analysis"
+title: "Hate Crimes in Toronto: Increasing Hates Towards Jewish People and Growing Incidents in Public Spaces"
 author: "Boxuan Yi"
 format: pdf
+abstract: "Hate crimes data are important tools for understanding underlying biases and social dynamics.
+In this paper, I analyze data from Open Data Toronto on hate crimes from 2018 to 2023.
+The findings reveal that Jewish people are the most frequently targeted, with incidents still on the rise, followed by Black individuals.
+Additionally, about half of these crimes occurred in public spaces or transportation, with an increasing trend in educational and commercial/business settings."
+date: "20 September 2024"
+date-format: "D MMMM YYYY"
+number-sections: true
+thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/hate_crimes_in_toronto"
+bibliography: references.bib
+toc: true
 ---
-Paper 1
+\newpage
+# Introduction {#sec-introduction}
 ```{r}
@@
 ```
+The issue of hate crimes is a global concern.
+Hate crimes are typically defined as criminal offences committed against a person or property based solely on the victim’s identity, such as race, religion, nationality, ethnic origin, sexual orientation, gender, or disability [@justice].
+These crimes not only harm the individual victims but also create an atmosphere of fear and division within society.
+As one of the most diverse cities in the world, Toronto is experiencing a rising number of hate crimes, which has raised significant public concern.
+This trend highlights the urgent need for effective interventions that can address the root causes of such crimes.
+To better allocate resources and reduce hate, it is important to analyze hate crimes data—specifically, whether criminals are targeting particular groups and, if so, which ones.
 
+This paper utilizes data from Open Data Toronto to explore the distribution of hate crimes by bias and location from 2018 to 2023.
+The biases examined include race, religion, and mental or physical disability.
+The locations considered are various regions in Toronto and different types of settings where the crimes occur.
+The results show that a significant proportion of hate crimes were directed at Black individuals and Jewish people, accounting for approximately 16% and 31% of incidents, respectively.
+About half of the crimes occurred in public spaces or transportation and about half were property crimes, with increasing trends observed in educational and commercial/business settings.
+
+The structure of this paper is as follows: The data utilized for analysis is introduced in @sec-data.
+Following that, @sec-results presents visualizations and analysis of the data.
+@sec-discussion then discusses the findings in a broader context, addresses limitations and outlines potential next steps.
+This analysis is conducted using the programming language R [@r] and the following packages: `opendatatoronto` [@ropendatatoronto], `dplyr` [@rdplyr], `tidyverse` [@rtidyverse], `here` [@rhere], `janitor` [@rjanitor], `knitr` [@rknitr], `ggplot2` [@rggplot2].
+
+# Data {#sec-data}
+## Data Overview and Measurement
+A hate crime is a criminal offence committed against a person motivated by bias and prejudice [@opendatatoronto].
+This analysis uses the Hate Crimes Open Data downloaded from Open Data Toronto to analyze the bias behind hate crimes and the location of offence.
+It contains all verified hate crime occurrences from 2018 to 2023, with annual updates.
+The dataset categorizes crimes based on age, mental or physical disability, race, ethnicity, language, religion, sexual orientation, and gender.
+
+The variables or measurements included in the dataset are ID, occurrence time (time, date and year), reported time (time, date and year), police division, location type, and various bias categories (age, disability, race, ethnicity, language, religion, sexual orientation, and gender), the primary offence related to the hate crime, neighbourhood, and arrest status.
+I also created two new variables: `occurrence month`, derived from the occurrence date, and `division area`, which groups the 16 police divisions and NSA into 5 regions of Toronto, with an additional ‘Other’ category.
+
+The raw dataset contains 1350 hate crimes.
+After cleaning the data, 1287 rows remain.
+This analysis mainly focuses on biases related to disability, race, and religion, as well as the time and location of hate crimes.
+
+## Data Cleaning
+Missing values are removed from the dataset. A new column for the occurrence month is created by extracting the month from the `occurrence_date`.
+
+The `religion_bias` column is cleaned by consolidating various Christian denominations into a single ‘Christian’ category, while mixed biases were excluded.
+Similarly, the unclear values in the `race_bias` column, such as ‘Black, South Asian’, was removed.
+The `location_type` column was regrouped to simplify the categorization.
+A new column `primary_offence_simplified` was created to group primary offenses into major categories like ‘Assault’ and ‘Property Crimes’.
+Finally, the dataset was modified to include a simplified `division_area` column based on police divisions.
+
+# Results {#sec-results}
 ```{r}
@@
 ```
+@fig-month is an overview of the occurrence of hate crimes in each month, in which shows that June has the most number of crimes, over 150 cases.
+The time period with the second highest number of crimes happen in September and October, with numbers decreasing to the lowest in winter, as in December, January and February there are the least number of hate crimes.
 
+@fig-race illustrates the trend in hate crimes by race bias from 2018 to 2023.
+The majority of these crimes do not show a specific racial bias.
+Among those that do, the most frequent targets are Black individuals.
+The figure indicates a sharp rise in hate crimes from 2019 to 2020, followed by another significant increase between 2022 and 2023.
+Hate crimes targeting Black individuals increased significantly starting in 2020, with a slight decline in 2023.
+Similarly, there was a sharp rise in crimes against East and Southeast Asian communities in 2021, followed by a decline in 2022 and 2023.
+Hate crimes against South Asian individuals also experienced an increase beginning in 2021.
 ```{r}
@@
 
+\newpage
+@fig-religion presents the trend in hate crimes motivated by religious bias from 2018 to 2023.
+Compared to race bias, the proportion of ‘None’ is smaller, indicating that a higher percentage of hate crimes are driven by religious bias.
+Each year, approximately half of these crimes targeted Jewish individuals, with a significant increase observed from 2022 to 2023.
+The proportion of crimes targeting Muslims declined after 2020 but showed an increase again in 2023.
+Additionally, there was a relatively higher number of crimes against Catholics in 2020.
 ```{r}
@@
 
+As shown in @fig-location_year, the most common location type for hate crimes is public spaces/transportation, followed by educational and residential areas.
+A sudden increase of crimes in public spaces/transportation took place in 2020, remaining until 2023.
+In 2022 and 2023, the number of hate crimes in educational settings increased, and crimes in commercial/business buildings rose in 2023 as well.
 ```{r}
@@
 data_cleaned |>
-  ggplot(mapping = aes(x = occurrence_year, fill = location_type)) +
-  geom_bar() +
-  labs(x = "Year Offence Occured", y = "Number of Observations", fill = "Location Type of the Offence") +
-  theme(legend.position = "right") +
-  scale_x_continuous(breaks = seq(2018, 2023, by = 1))
+  group_by(occurrence_year, location_type) |>
+  summarise(Count = n(), .groups = 'drop') |>
+  ggplot(mapping = aes(x = occurrence_year, y = Count, color = location_type)) +
+  geom_point(size = 2) +
+  theme_light() +
+  labs(
+    x = "Year Offence Occurred", 
+    y = "Number of Observations", 
+    title = "Distribution of Hate Crimes by Location Type"
+  ) +
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(plot.title = element_text(face = "bold")) +
+  scale_x_continuous(breaks = seq(2018, 2023, by = 1)) +
+  scale_color_brewer(palette = "Paired")
 ```
 
+@fig-location (a) depicts the distribution of hate crimes by location type and division area.
+The Toronto-East York region had the highest number of crimes, followed by North York, Etobicoke-York, Scarborough, with Etobicoke experiencing the fewest.
+Similarly, public spaces/transportation had the highest crime rates, particularly in the Toronto-East York and Etobicoke regions.
+Residential crimes were more prevalent in North York and Etobicoke-York, while educational crimes were more common in Scarborough and North York.
+Crimes in commercial/business settings were notably higher in Toronto-East York, while religious crimes were more frequent in Etobicoke-York.
+@fig-location (b) displays the distribution of hate crimes by primary offence and location type.
+Property crimes were the most common offence across all locations except for public spaces/transportation, where assault was the most frequent offence.
+Threats and harassment also constituted a significant proportion of crimes, particularly in residential and commercial buildings.
 ```{r}
@@
   theme(legend.position = "right") +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
+  scale_fill_brewer(palette = "Set3")
 
@@
   theme(legend.position = "right") +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+  theme(axis.text.x = element_text(angle = 50, hjust = 1)) + 
+  scale_fill_brewer(palette = "Set3")
 ```
 
+\newpage
+As shown in @tbl-disability, only 3 out of 1287 hate crimes were motivated by disability bias, which is quite low compared to other factors like religion and race.
 ```{r}
@@
 
+@tbl-all highlights the proportions of hate crimes targeting six groups, which are age, mental or physical disability, religion, race, gender, and sexual orientation.
+The most significant proportion of hate crimes targeted Jewish individuals, accounting for 31.2% of cases, with no biases related to race, gender, or sexual orientation.
+Black individuals experienced the second-highest proportion at 16.1%, followed by incidents where no specific bias was identified at 10.9%.
+Hate crimes against Muslim individuals constituted 7.4% of the total.
+Crimes targeting individuals based on sexual orientation, particularly those identifying as gay or 2SLGBTQ+, represented a combined 11.1% of incidents.
+Other notable proportions include crimes against East/Southeast Asian individuals at 4.6% and South Asian individuals at 1.5%.
 ```{r}
@@
 #| warning: false
-#| label: tbl-clean_mci_data
-#| tbl-cap: The Number of Hate Crimes Based on Suspect’s Perception of Victim’s Age
-data_cleaned |>
-  group_by(age_bias) |>
-  summarise(count = n()) |>
-  rename("Age Bias" = age_bias, "Count" = count) |>
+#| label: tbl-all
+#| tbl-cap: The Proportion of Hate Crimes Based on Six Factors
+data_cleaned %>%
+  group_by(age_bias, mental_or_physical_disability, religion_bias, race_bias, sexual_orientation_bias, gender_bias) %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(proportion = count / sum(count)) %>%
+  arrange(desc(proportion)) %>%
+  select("Age Bias" = age_bias, 
+         "Mental or Physical Disability" = mental_or_physical_disability, 
+         "Religion Bias" = religion_bias, 
+         "Race Bias" = race_bias, 
+         "Gender Bias" = gender_bias, 
+         "Sexual Orientation Bias" = sexual_orientation_bias, 
+         "Proportion" = proportion) %>%
+  head(10) %>%
   kable()
 ```
+# Discussion {#sec-discussion}
+## Race and Religion Biases
+Hate crimes in Toronto involving race and religion biases are often influenced by global and local events.
+The rise in hate crimes against East and Southeast Asian communities during 2020 and 2021 could be attributed to the outbreak of COVID-19.
+As the pandemic spread, harmful stereotypes and misinformation may lead to xenophobia and hate.
+This resulted in a surge of racially motivated hate crimes, reflecting a pattern of pandemic-related discrimination seen in many places around the world.
+The return to normal life in 2022 and 2023 could be a large reason contributed to the reduction in hate incidents.
+Similarly, the sharp rise in hate crimes against Black individuals from 2019 to 2020 coincides with heightened racial tensions and movements like Black Lives Matter, which gained global attention after incidents of police brutality.
+The significant increase in hate crimes targeting Jewish communities in 2023 appears to be tied to the Israeli-Palestinian conflict.
+There were numerous parades and protests in Toronto last year.
+As attention on the Israeli-Palestinian conflict increased, it is likely that some individuals committed hate crimes against Jewish people in response.
+The increase in anti-Muslim hate crimes in 2023 could be related to similar international dynamics or to ongoing Islamophobia that has been exacerbated by media portrayal of global events.
+In 2020, some controversies involving the Catholic Church, such as discussions around clerical abuse scandals or abortion, could have intensified negative sentiments toward Catholics, causing an increasing number of hate crimes towards this community.
+
+## Regions and Locations
+The prevalence of hate crimes in public spaces and transportation can be attributed to several factors.
+First, these areas are easily accessible and often crowded, allowing individuals to commit crimes with less fear of being identified.
+Second, the crowded environment makes it easier to carry out random acts of violence, such as pushing someone onto a subway track.
+The rise in hate crimes in residential and educational settings in 2022 and 2023 may be linked to the economic and social pressures experienced after the pandemic.
+The Toronto-East York region, with its large population, naturally has a higher number of hate crimes, particularly in public and commercial locations.
+The presence of numerous commercial buildings and public transportation options contributes to this trend.
+The prevalence of residential crimes in North York and Etobicoke-York may also be due to the significant number of residential constructions in these regions.
+Since assaults are easier to commit in public spaces rather than private areas, it makes sense that property crimes are the most common offences across all locations, except for public spaces and transportation, where assaults are more frequent.
+Furthermore, the fact that most hate crimes are property crimes can be linked to the observation that more than half of these incidents are not motivated by bias, as stealing from anyone is essentially the same.
+
+## Limitation
+This dataset only includes confirmed hate crimes and does not account for occurrences deemed unfounded or classified as hate incidents.
+Additionally, some hate crimes may go unreported due to victim fear or distrust in law enforcement, causing potential biases.
+For instance, crimes that occur in households might be underrepresented, as victims may feel more vulnerable knowing the perpetrator has access to their home address, unlike crimes committed in public spaces.
+Furthermore, the dataset, covering only the years from 2018 to 2023, may overlook long-term trends and patterns in hate crimes.
+
+## Next steps
+To effectively reduce hate crimes, it would be beneficial to collect data on the motivations behind these incidents.
+Understanding the differences between property crimes and those explicitly targeting individuals based on bias could provide valuable insights.
+
+While most victims report hate crimes within a day, some do not report until ten days later,.
+Future research could focus on the reasons behind delayed reporting and the factors contributing to victim fear.
+Collaborating with local organizations and advocacy groups could enhance support for affected communities and help develop targeted prevention strategies.
+
+\newpage
+# References

### 2024-09-21 scripts/01-download_data.R

@@ -6,7 +6,7 @@
 # Prerequisites: None
 
 # install.packages('opendatatoronto')
-# install.packages('dylyr')
+# install.packages('dplyr')
 # install.packages('tidyverse')
 # install.packages('here')
 # install.packages('janitor')

### 2024-09-21 scripts/02-clean_data.R

@@ -59,7 +59,7 @@ data_cleaned <- data_cleaned |>
 # Create a simplified column that describes the primary offence
 data_cleaned <- data_cleaned |>
   mutate(primary_offence_simplified = case_when(
-    primary_offence %in% c("Wilful Promotion of Hatred", "Public Incitement of Hatred", "Advocating Genocide") ~ "Hate Crimes",
+    primary_offence %in% c("Wilful Promotion of Hatred", "Public Incitement of Hatred", "Advocating Genocide") ~ "Hatred",
     primary_offence %in% c("Assault", "Assault With a Weapon", "Assault Causing Bodily Harm", "Assault Peace Officer", "Aggravated Assault") ~ "Assault",
     primary_offence %in% c("Mischief Under $5000", "Mischief Interfere With Property", "Mischief To Religious Property, Educational Institutions, Etc.", "Mischief Over $5000", "Mischief To Data", "Arson", "Theft", "Robbery") ~ "Property Crimes",
     primary_offence %in% c("Uttering Threats - Bodily Harm", "Uttering Threats - Property", "Criminal Harassment", "Harassing Communications", "Disturbing Religious Worship Or Certain Meetings", "Causing a Disturbance") ~ "Threats and Harassment",

### 2024-09-22 output/paper.qmd
correct minor mistakes in the paper

--- 2024-09-20 output/paper.qmd
@@
 ---
-title: "toronto_fire_incidents_analysis"
+title: "Hate Crimes in Toronto: Increasing Hates Towards Jewish People and Growing Incidents in Public Spaces"
 author: "Boxuan Yi"
 format: pdf
+abstract: "Hate crime data provide crucial insights into underlying biases and social dynamics.
+This paper uses data from Open Data Toronto to analyze the distribution of hate crimes from 2018 to 2023, focusing on biases and locations.
+The findings reveal that Jewish people are the most frequently targeted, with incidents continuing to rise, followed by Black individuals.
+Additionally, nearly half of the crimes occurred in public spaces or transportation."
+date: "22 September 2024"
+date-format: "D MMMM YYYY"
+number-sections: true
+thanks: "Code and data in this analysis is available at: https://github.com/Elaineyi1/hate_crimes_in_toronto"
+bibliography: references.bib
+toc: true
 ---
-Paper 1
+\newpage
+# Introduction {#sec-introduction}
 ```{r}
@@
 ```
+The issue of hate crimes is a global concern.
+Hate crimes are typically defined as criminal offences committed against a person or property based solely on the victim’s identity, such as race, religion, sexual orientation, gender, or disability [@justice].
+Beyond the harm they inflict on individual victims, hate crimes foster fear and division within society.
+As one of the world’s most diverse cities, Toronto has experienced a rising number of hate crimes, which prompts widespread public concern.
+This trend highlights the urgent need for effective interventions that can address the root causes of such crimes.
+To better reduce hate incidents and develop strategies, it is important to analyze hate crime data — specifically, whether criminals are targeting particular groups and, if so, which ones.
 
+This paper utilizes data from Open Data Toronto to explore the distribution of hate crimes by bias and location from 2018 to 2023.
+The biases examined include race, religion, and mental or physical disability.
+The locations considered are various regions in Toronto and different types of settings where crimes occur.
+The results show that a significant proportion of hate crimes were directed at Black individuals and Jewish people, accounting for approximately 16% and 31% of incidents, respectively.
+About half of the crimes occurred in public spaces or transportation, and about half were property crimes, with increasing trends observed in educational and commercial/business settings.
+
+The structure of this paper is as follows: The data utilized for analysis is introduced in @sec-data.
+Following that, @sec-results presents visualizations and analysis of the data.
+@sec-discussion then discusses the findings in a broader context, addresses limitations and outlines potential next steps.
+This analysis is conducted using the programming language R [@r] and the following packages: `opendatatoronto` [@ropendatatoronto], `dplyr` [@rdplyr], `tidyverse` [@rtidyverse], `here` [@rhere], `janitor` [@rjanitor], `knitr` [@rknitr], `ggplot2` [@rggplot2].
+
+# Data {#sec-data}
+## Data Overview and Measurement
+A hate crime is a criminal offence committed against a person motivated by bias and prejudice [@hatecrime].
+This analysis uses hate crime data from Open Data Toronto, covering verified hate crime occurrences from 2018 to 2023, updated annually.
+The dataset categorizes crimes by various bias types, such as age, disability, race, ethnicity, language, religion, sexual orientation, and gender.
+Provided by the Toronto Police Service, this dataset aims to enhance community awareness and public safety [@police].
+
+The variables or measurements included in the dataset are ID, occurrence time (time, date and year), reported time (time, date and year), police division, location type, various bias categories (age, disability, race, ethnicity, language, religion, sexual orientation, and gender), the primary offence related to the hate crime, neighbourhood, and arrest status.
+I also created two new variables: `occurrence_month`, derived from the occurrence date, and `division_area`, which groups the 17 police divisions, including 'NSA', into 5 regions of Toronto, with an additional 'Other' category.
+The data is provided at the occurrence level.
+The location of Hate Crime occurrences have been grouped to the neighbourhood level to protect the privacy of parties and communities involved in the occurrence.
+
+The raw dataset contains 1350 hate crimes.
+After cleaning, 1287 rows remain.
+This analysis mainly focuses on biases related to disability, race, and religion, as well as the time and location of hate crimes.
+
+## Data Cleaning
+Missing values have been removed from the dataset. A new column `occurrence_month` has been created by extracting the month from the `occurrence_date`.
+
+The `religion_bias` column has been cleaned by consolidating various Christian denominations into a single ‘Christian’ category, while mixed biases have been excluded.
+Similarly, the unclear values in the `race_bias` column, such as ‘Black, South Asian’, have been removed.
+The `location_type` column has been regrouped to simplify the categorization.
+Additionally, a new column `primary_offence_simplified` has been mutated to group primary offenses into major categories, such as ‘Assault’ and ‘Property Crimes’.
+Finally, the dataset has been modified to include a simplified `division_area` column based on police divisions.
+
+# Results {#sec-results}
 ```{r}
@@
 #| fig-cap: Monthly Occurrences of Hate Crimes in Toronto From 2018 to 2023
+#| fig-width: 3
+#| fig-height: 2
 data_cleaned |>
@@
   theme_minimal()
+```
+@fig-month provides an overview of hate crime occurrences by month, showing that June has the highest number of crimes, with over 150 cases.
+The second-highest number of crimes occurs in September and October, with numbers decreasing to their lowest in winter, as December, January, and February see the fewest hate crimes.
 
-```
+@fig-race illustrates the trend in hate crimes by racial bias from 2018 to 2023.
+The figure shows a sharp increase in hate crimes from 2019 to 2020, followed by another significant rise between 2022 and 2023.
+Most of these crimes do not demonstrate a specific racial bias; however, among those that do, Black individuals are the most frequent targets.
+Hate crimes targeting Black individuals notably surged starting in 2020, with a slight decline in 2023.
+There was also a marked rise in crimes against East and Southeast Asian communities in 2021, followed by declines in 2022 and 2023.
+Additionally, hate crimes against South Asian individuals began to increase slightly in 2021.
 
@@
 ```
-
+@fig-religion presents the trend in hate crimes motivated by religious bias from 2018 to 2023.
+Compared to race bias, the proportion of crimes categorized as ‘None’ is smaller, indicating that a higher percentage of hate crimes are driven by religious motivations.
+Each year, nearly half of these crimes targeted Jewish individuals, with a significant increase observed from 2022 to 2023.
+The proportion of crimes targeting Muslims declined after 2020 but showed an increase again in 2023.
+Additionally, a relatively higher number of crimes against Catholics is also observed in 2020.
 ```{r}
@@
 #| fig-cap: Trends in Hate Crimes by Religion Bias From 2018 to 2023
+#| fig-width: 5
+#| fig-height: 2.5
 data_cleaned |>
@@
 ```
-
+\newpage
+As shown in @fig-location_year, the most common location type for hate crimes is public spaces/transportation, followed by educational and residential areas.
+A sudden increase in crimes in public spaces/transportation occurred in 2020, remaining high until 2023.
+Starting in 2021, the number of hate crimes in educational settings increased.
+Crimes in commercial/business, government and religions buildings all rose in 2023.
 ```{r}
@@
 #| fig-cap: Trends in Hate Crimes by Location Type of the Offence From 2018 to 2023
+#| fig-height: 2.8
 data_cleaned |>
-  ggplot(mapping = aes(x = occurrence_year, fill = location_type)) +
-  geom_bar() +
-  labs(x = "Year Offence Occured", y = "Number of Observations", fill = "Location Type of the Offence") +
-  theme(legend.position = "right") +
-  scale_x_continuous(breaks = seq(2018, 2023, by = 1))
+  group_by(occurrence_year, location_type) |>
+  summarise(Count = n(), .groups = 'drop') |>
+  ggplot(mapping = aes(x = occurrence_year, y = Count, color = location_type)) +
+  geom_point(size = 2) +
+  theme_light() +
+  labs(x = "Year Offence Occurred", y = "Number of Observations", color = "Location Type") +  # Changed 'fill' to 'color'
+  guides(color = guide_legend(override.aes = list(size = 3))) +
+  theme(plot.title = element_text(face = "bold")) +
+  scale_x_continuous(breaks = seq(2018, 2023, by = 1)) +
+  scale_color_brewer(palette = "Paired")
+
 ```
+\newpage
+@fig-location (a) shows the distribution of hate crimes by location type and division area.
+The Toronto-East York region recorded the highest number of crimes, followed by North York, Etobicoke-York, and Scarborough, with Etobicoke seeing the fewest.
+Similar to @fig-location_year, public spaces and transportation had the most crimes, particularly in Toronto-East York and Etobicoke.
+Residential crimes were more prevalent in North York and Etobicoke-York, while educational settings saw higher crime rates in Scarborough and North York.
+Crimes in commercial/business settings were notably higher in Toronto-East York, while religious crimes were more frequent in Etobicoke-York.
+
+@fig-location (b) displays the distribution of hate crimes by primary offence and location type.
+Property crimes were overwhelmingly the most common offense across all locations, except for public spaces and transportation, where assault occurred at nearly the same rate.
+Threats and harassment also contributed to a significant portion of crimes, particularly in residential and commercial buildings.
 
@@
   theme(legend.position = "right") +
-  theme(axis.text.x = element_text(angle = 30, hjust = 1))
+  theme(axis.text.x = element_text(angle = 50, hjust = 1)) + 
+  scale_fill_brewer(palette = "Set3")
 ```
 
+\newpage
+As shown in @tbl-disability, only 3 out of 1,287 hate crimes were motivated by disability bias, a significantly lower number compared to other factors such as religion and race.
 ```{r}
@@
 #| warning: false
-#| label: tbl-clean_mci_data
-#| tbl-cap: The Number of Hate Crimes Based on Suspect’s Perception of Victim’s Age
-data_cleaned |>
-  group_by(age_bias) |>
-  summarise(count = n()) |>
-  rename("Age Bias" = age_bias, "Count" = count) |>
+#| label: tbl-all
+#| tbl-cap: The Proportion of Hate Crimes Based on Six Factors
+data_cleaned %>%
+  group_by(age_bias, mental_or_physical_disability, religion_bias, race_bias, sexual_orientation_bias, gender_bias) %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  mutate(proportion = count / sum(count)) %>%
+  arrange(desc(proportion)) %>%
+  select("Age Bias" = age_bias, 
+         "Mental or Physical Disability" = mental_or_physical_disability, 
+         "Religion Bias" = religion_bias, 
+         "Race Bias" = race_bias, 
+         "Gender Bias" = gender_bias, 
+         "Sexual Orientation Bias" = sexual_orientation_bias, 
+         "Proportion" = proportion) %>%
+  head(10) %>%
   kable()
 ```
+# Discussion {#sec-discussion}
+## Race and Religion Biases
+Hate crimes in Toronto involving race and religion biases are often influenced by global and local events.
+The rise in hate crimes against East and Southeast Asian communities during 2020 and 2021 could be attributed to the outbreak of COVID-19.
+As the pandemic spread, harmful stereotypes and misinformation likely led to xenophobia and hate.
+This resulted in a surge of racially motivated hate crimes, reflecting a pattern of pandemic-related discrimination seen in many places around the world.
+The return to normal life in 2022 and 2023 could contribute to the reduction in hate incidents.
+Similarly, the sharp rise in hate crimes against Black individuals from 2019 to 2020 coincides with heightened racial tensions and movements like Black Lives Matter, which gained global attention following incidents of police brutality.
+The significant increase in hate crimes targeting Jewish communities in 2023 appears to be tied to the Israeli-Palestinian conflict.
+Numerous parades and protests took place in Toronto last year, and as attention on the conflict grew, it is likely that some individuals committed hate crimes against Jewish people in response.
+The rise in anti-Muslim hate crimes in 2023 could be related to similar international dynamics or to ongoing Islamophobia exacerbated by media portrayals of global events.
+In 2020, controversies involving the Catholic Church, such as discussions around clerical abuse scandals or abortion, may have intensified negative sentiments toward Catholics, leading to an increase in hate crimes against this community.
+
+## Regions and Locations
+The prevalence of hate crimes in public spaces and transportation can be attributed to several factors.
+First, these areas are easily accessible and often crowded, allowing individuals to commit crimes with less fear of being identified.
+Second, the crowded environment makes it easier to carry out random acts of violence, such as pushing someone onto a subway track.
+The Toronto-East York region, with its large population, naturally has a higher number of hate crimes, particularly in public and commercial locations.
+The presence of numerous commercial buildings and public transportation options contributes to this trend.
+The prevalence of residential crimes in North York and Etobicoke-York may also be due to the significant amount of residential development in these regions.
+Since assaults are easier to commit in public spaces than in private areas, it follows that property crimes are the most common offences across all locations, except for public spaces and transportation, where assaults are as frequent as property crimes.
+Furthermore, the fact that most hate crimes are property crimes may be linked to the economic and social pressures experienced after the pandemic.
+
+## Limitation
+This dataset only includes confirmed hate crimes and does not account for occurrences deemed unfounded or classified as hate incidents.
+Additionally, some hate crimes may go unreported due to victim fear or distrust of law enforcement, causing potential biases.
+For instance, crimes occurring in households might be underrepresented, as victims may feel more vulnerable knowing the perpetrator has access to their home address, unlike crimes committed in public spaces.
+Furthermore, the dataset, covering only the years from 2018 to 2023, may overlook long-term trends in hate crimes.
+
+## Next steps
+To effectively reduce hate crimes, it would be beneficial to collect data on the motivations behind these incidents.
+Understanding the differences between property crimes and those explicitly targeting individuals based on bias could provide valuable insights.
+
+While most victims report hate crimes within a day, some do not report until ten days later.
+Future research could focus on the reasons behind delayed reporting and the factors contributing to victim fear.
+Collaborating with local organizations and advocacy groups could enhance support for affected communities and help develop targeted prevention strategies.
+
+\newpage
+# References

### 2024-09-26 output/paper.qmd
final version

@@
 ---
-title: "Hate Crimes in Toronto: Increasing Hates Towards Jewish People and Growing Incidents in Public Spaces"
+title: "Rising Hate Crimes in Toronto: Increased Targeting of Jewish People and Public Incidents"
 author: "Boxuan Yi"
 format: pdf
-abstract: "Hate crime data provide crucial insights into underlying biases and social dynamics.
-This paper uses data from Open Data Toronto to analyze the distribution of hate crimes from 2018 to 2023, focusing on biases and locations.
-The findings reveal that Jewish people are the most frequently targeted, with incidents continuing to rise, followed by Black individuals.
-Additionally, nearly half of the crimes occurred in public spaces or transportation."
-date: "22 September 2024"
+abstract: "Hate crime data provide valuable insights into underlying biases and social dynamics.
+This paper analyzes hate crime reports from Open Data Toronto between 2018 and 2023, focusing on the distribution of crimes by target group and location.
+The analysis reveals that Jewish people are the most frequently targeted group, followed by Black individuals, and the number of incidents continues to rise.
+Additionally, nearly half of hate crimes occur in public spaces/transportation, highlighting the growing threat to safety in everyday environments."
+date: "26 September 2024"
 date-format: "D MMMM YYYY"
@@
 Beyond the harm they inflict on individual victims, hate crimes foster fear and division within society.
-As one of the world’s most diverse cities, Toronto has experienced a rising number of hate crimes, which prompts widespread public concern.
-This trend highlights the urgent need for effective interventions that can address the root causes of such crimes.
-To better reduce hate incidents and develop strategies, it is important to analyze hate crime data — specifically, whether criminals are targeting particular groups and, if so, which ones.
+As one of the world’s most diverse cities, Toronto has experienced a rising number of hate crimes, prompting widespread public concern.
+This trend underscores the urgent need for effective interventions that can address the root causes of such crimes.
+To better reduce hate incidents and develop strategies, it is important to analyze hate crime data — specifically, to determine whether criminals are targeting particular groups and, if so, which ones.
 
-This paper utilizes data from Open Data Toronto to explore the distribution of hate crimes by bias and location from 2018 to 2023.
-The biases examined include race, religion, and mental or physical disability.
-The locations considered are various regions in Toronto and different types of settings where crimes occur.
+This paper seeks to fill this gap by analyzing hate crime data from Open Data Toronto, spanning 2018 to 2023.
+The goal is to identify which biased groups, including those based on race, religion, and disability, are most frequently targeted, and to examine the locations and types of settings where these crimes occur.
 The results show that a significant proportion of hate crimes were directed at Black individuals and Jewish people, accounting for approximately 16% and 31% of incidents, respectively.
-About half of the crimes occurred in public spaces or transportation, and about half were property crimes, with increasing trends observed in educational and commercial/business settings.
+About half of the crimes occurred in public spaces or on transportation, and roughly half were property crimes, with increasing trends observed in educational and commercial/business settings.
+These trends not only highlight the vulnerability of these groups but also point to an increasing threat in everyday public environments, emphasizing the need for stronger interventions.
 
@@
 ## Data Overview and Measurement
-A hate crime is a criminal offence committed against a person motivated by bias and prejudice [@hatecrime].
-This analysis uses hate crime data from Open Data Toronto, covering verified hate crime occurrences from 2018 to 2023, updated annually.
-The dataset categorizes crimes by various bias types, such as age, disability, race, ethnicity, language, religion, sexual orientation, and gender.
-Provided by the Toronto Police Service, this dataset aims to enhance community awareness and public safety [@police].
+A hate crime is a criminal offense committed against a person, motivated by bias and prejudice [@hatecrime].
+The hate crime data used in this analysis is sourced from Open Data Toronto, provided by the Toronto Police Service and updated annually.
+This data is collected through victim reports.
+It contains all verified hate crime occurrences from 2018 to 2023, aiming to enhance community awareness and public safety [@police].
+The dataset categorizes crimes based on various bias types, including age, disability, race, ethnicity, language, religion, sexual orientation, and gender.
+The data is provided at the occurrence level.
 
-The variables or measurements included in the dataset are ID, occurrence time (time, date and year), reported time (time, date and year), police division, location type, various bias categories (age, disability, race, ethnicity, language, religion, sexual orientation, and gender), the primary offence related to the hate crime, neighbourhood, and arrest status.
+The variables included in the dataset are ID, occurrence time (time, date and year), reported time (time, date and year), police division, location type, various bias categories (age, disability, race, ethnicity, language, religion, sexual orientation, and gender), the primary offence related to the hate crime, neighborhood, and arrest status.
 I also created two new variables: `occurrence_month`, derived from the occurrence date, and `division_area`, which groups the 17 police divisions, including 'NSA', into 5 regions of Toronto, with an additional 'Other' category.
-The data is provided at the occurrence level.
-The location of Hate Crime occurrences have been grouped to the neighbourhood level to protect the privacy of parties and communities involved in the occurrence.
+The location of Hate Crime occurrences have been grouped to the neighborhood level to protect the privacy of parties and communities involved in the occurrence [@police].
 
+This analysis mainly focuses on biases related to disability, race, and religion, as well as the time and location of hate crimes.
 The raw dataset contains 1350 hate crimes.
 After cleaning, 1287 rows remain.
-This analysis mainly focuses on biases related to disability, race, and religion, as well as the time and location of hate crimes.
+This dataset is the only one related to hate crimes available on Open Data Toronto, so no other similar datasets could have been used.
 
 ## Data Cleaning
-Missing values have been removed from the dataset. A new column `occurrence_month` has been created by extracting the month from the `occurrence_date`.
+Missing values have been removed from the dataset.
+A new column `occurrence_month` has been created by extracting the month from the `occurrence_date`.
+The dataset has been modified to include a simplified `division_area` column based on police divisions.
 
@@
 Additionally, a new column `primary_offence_simplified` has been mutated to group primary offenses into major categories, such as ‘Assault’ and ‘Property Crimes’.
-Finally, the dataset has been modified to include a simplified `division_area` column based on police divisions.
+
+The number of unclear or mixed values in the biases is small, so they have been excluded from the analysis. The limitations of this exclusion will be discussed in @sec-discussion.
 
@@
 #| label: fig-month
-#| fig-cap: Monthly Occurrences of Hate Crimes in Toronto From 2018 to 2023
+#| fig-cap: Hate Crime Occurrences in Toronto by Month from 2018 to 2023
 #| fig-width: 3
@@
 
+\newpage
 @fig-race illustrates the trend in hate crimes by racial bias from 2018 to 2023.
@@
 #| fig-cap: Trends in Hate Crimes by Race Bias From 2018 to 2023
+#| fig-width: 6
+#| fig-height: 3
 data_cleaned |>
@@
 ```
+\newpage
 @fig-religion presents the trend in hate crimes motivated by religious bias from 2018 to 2023.
@@
 #| fig-cap: Trends in Hate Crimes by Religion Bias From 2018 to 2023
-#| fig-width: 5
-#| fig-height: 2.5
 data_cleaned |>
@@
 ```
-\newpage
 @fig-location (a) shows the distribution of hate crimes by location type and division area.
@@
 #| layout-ncol: 1
-#| fig-subcap: ["Distribution of Hate Crimes by Division Area and Location Type", "Distribution of Primary Offence by Location Type"]
+#| fig-subcap: ["Distribution of Hate Crimes by Division Area and Location Type From 2018 to 2023", "Distribution of Primary Offence by Location Type From 2018 to 2023"]
 
@@
 Similarly, the sharp rise in hate crimes against Black individuals from 2019 to 2020 coincides with heightened racial tensions and movements like Black Lives Matter, which gained global attention following incidents of police brutality.
+
 The significant increase in hate crimes targeting Jewish communities in 2023 appears to be tied to the Israeli-Palestinian conflict.
@@
 
+Providing resources and support for communities targeted by hate crimes, including counseling services, legal assistance, and community rebuilding initiatives, can help mitigate the effects of these crimes and strengthen community resilience.
+Implementing educational campaigns aimed at raising awareness about hate crimes, their impacts, and the importance of diversity and inclusion can also foster understanding within communities.
+
 ## Regions and Locations
@@
 Second, the crowded environment makes it easier to carry out random acts of violence, such as pushing someone onto a subway track.
-The Toronto-East York region, with its large population, naturally has a higher number of hate crimes, particularly in public and commercial locations.
-The presence of numerous commercial buildings and public transportation options contributes to this trend.
-The prevalence of residential crimes in North York and Etobicoke-York may also be due to the significant amount of residential development in these regions.
 Since assaults are easier to commit in public spaces than in private areas, it follows that property crimes are the most common offences across all locations, except for public spaces and transportation, where assaults are as frequent as property crimes.
 Furthermore, the fact that most hate crimes are property crimes may be linked to the economic and social pressures experienced after the pandemic.
+
+The Toronto-East York region, with its large population, naturally reports a higher number of hate crimes.
+The presence of numerous commercial buildings and public transportation options contributes to the trend of elevated crime rates in public and commercial locations within Toronto-East York.
+The prevalence of residential crimes in North York and Etobicoke-York may also be due to the significant amount of residential development in these regions.
 
@@
 Furthermore, the dataset, covering only the years from 2018 to 2023, may overlook long-term trends in hate crimes.
+
+As illustrated in @sec-data, there is a small number of unclear biases in the dataset.
+These unclear values, such as "Black, South Asian" in the religion bias column, have been removed.
+This exclusion may lead to some biases being underreported, as all unclear values indicate a bias rather than a 'None' response.
 

### 2024-09-26 scripts/02-clean_data.R

@@ -14,6 +14,7 @@ library(knitr)
 # Read the raw dataset
 data_raw <- read_csv(file = here("../inputs/data/data_raw.csv"))
 
+# Clean the names, eliminate NA, and create an occurrence month column
 data_cleaned <- clean_names(data_raw)
 data_cleaned <- na.omit(data_cleaned)
 data_cleaned$occurrence_month <- as.numeric(substr(data_cleaned$occurrence_date, 6, 7))

### 2024-09-26 scripts/03-test_data.R

@@ -3,7 +3,7 @@
 # Author: Boxuan Yi
 # Email: boxuan.yi@mail.utoronto.ca
 # Date: 19 September 2024
-# Prerequisites: None
+# Prerequisites: Understand the tested dataset
 
 library(here)
 library(dplyr)

### 2024-09-27 output/paper.qmd
final

@@
 ---
-title: "Rising Hate Crimes in Toronto: Increased Targeting of Jewish People and Public Incidents"
+title: "Analysis of Hate Crimes in Toronto From 2018 to 2023"
+subtitle: "Increasing Targeting of Jewish People and Rising Public Incidents"
 author: "Boxuan Yi"
@@
 
-This paper seeks to fill this gap by analyzing hate crime data from Open Data Toronto, spanning 2018 to 2023.
+This paper seeks to fill this gap by analyzing hate crime data from Open Data Toronto, spanning 2018 to 2023 [@hatecrime].
 The goal is to identify which biased groups, including those based on race, religion, and disability, are most frequently targeted, and to examine the locations and types of settings where these crimes occur.
